\bf Range Analysis for the IonMonkey JavaScript engine

### 2012-05-02 project-writings/paper.tex
cite the ECMA spec

While the ECMA specification for Javascript requires that all numbers behave as
double-precision floating point values, for performance reasons JIT compilers
represent numbers as 32-bit integers when possible. However, since doubles can
represent larger values than integers, operations must be guarded against
overflow.  Our range analysis pass eliminates overflow checks when operations
can be proven not to overflow.

>>>>

While the ECMA specification for Javascript requires that all numbers behave as
double-precision floating point values\cite{ECMA-262}, for performance reasons JIT compilers
represent numbers as 32-bit integers when possible. However, since doubles can
represent larger values than integers, operations must be guarded against
overflow.  Our range analysis pass eliminates overflow checks when operations
can be proven not to overflow.
